\documentclass[a4paper]{article}

\title{Calculus/ Analysis Notes}
\input{header.tex}

\begin{document}
\maketitle

{\small \noindent\textbf{Foundations}\\
Sets and functions. Important properties, triangle inequalities. \hspace*{\fill} [6]

\vspace{10pt}
\noindent\textbf{Limits and Continuity}\\
Continuity of real-valued functions defined on subsets of $\R$. A continuous function on a closed bounded
interval is bounded and attains its bounds.\hspace*{\fill} [15]

\vspace{10pt}
\noindent\textbf{Important Theorems}\\
Intermediate Value Theorem, Extreme Value Theorem, etc.\hspace*{\fill} [5]

\vspace{10pt}
\noindent\textbf{Differentiation}\\
ifferentiability of functions from $\R$ to $\R$. Derivative of sums and
products. The chain rule. Derivative of the inverse function. Rolle's theorem;
the mean value theorem. One-dimensional version of the inverse function theorem.
Taylor's theorem from $\R$ to $\R$.\hspace*{\fill}[4]

\vspace{10pt}
\noindent\textbf{Integration}\\
Definition and basic properties of the Riemann integral. A non-integrable
function. Integrability of monotonic functions. Integrability of
piecewise-continuous functions. The fundamental theorem of calculus.
Differentiation of indefinite integrals. Integration by parts. The integral form
of the remainder in Taylor's theorem. Improper integrals.\hspace*{\fill} [6]}

\tableofcontents

\setcounter{section}{-1}
\section{Introduction}
In thise lecture notes, Calculus will be presented with rigor like Intro to
Analysis. Focusing on the definitions, theorems, and proofs instead of the
applications and intuition  of the topics. These notes are based on Spivak
Calculus

The notes will follow a the flow of Previous information, Motivation,
Formal statement, Proof, Corollaries, and Observations.

The notes are about Single-Variable Calculus

\input{Chapter 1 Foundations/Foundation.tex}
\input{Chapter 2 Limits and Continuity/LimCont.tex}

\end{document}