\pagebreak
\subsection{Number of Various Sorts}
\begin{defi}[Mathematical Induction] Suppose that $P(x)$ means that the property
$P$ holds for the number $x$. Then the principle of mathematical induction
states that $P(x)$ holds for all natural numbers $x$ provided that
\begin{itemize}
    \item $P(1)$ is true.
    \item Whenever $P(k)$ is true, $P(k+1)$ is true.
\end{itemize}     
\end{defi}

(Note: In the construction of the natural numbers from the \emph{Peano Axioms},
induction is an axiom and $0$ is an element of the naturals.)

\begin{defi}[Strong Induction] We use a stronger hypothesis since in some cases
it happens that in order to prove $P(k+1)$ we must assume not only $P(k)$, but
also $P(l)$ for all natural numbers $l \leq k$. $P(x)$ holds for all natural
numbers $x$ provideded that
\begin{itemize}
    \item $P(1)$ is true
    \item $P(k+1)$ is true, if $P(l)$ is true for $1<l \leq k$
\end{itemize}
\end{defi}

\begin{defi}[Recursive Definitions] A \emph{recursive definition} of a function
defines values of the function for some inputs in terms of the values of the
function for other inputs.
\end{defi}

For example, the number $n!$ is defined as the product of all then natural
numbers less then or equal to $n$:
\begin{equation*}
    n! = 1\ \cdot 2 \cdot 3 \cdot \dotsc \cdot (n-1) \cdot n.
\end{equation*} 
More formally:
\begin{align}
    1! &= 1 \\
    n!&=n\cdot (n-1)!.
\end{align}

Another example is the convenient notation regarding sums. Instead of writing 
\begin{equation*}
    a_1 + a_1 + \dotsb + a_n.
\end{equation*}
we will use the Greek letter $\Sigma$ and write
\begin{equation*}
    \sum \limits_{i=1}^{n} a_i. 
\end{equation*}

The define $\sum \limits_{i=1}^{n} a_i$ precisely really requires a recursive
definition:
\begin{align}
    \sum \limits_{i=1}^{1} a_i &= a_1, \\
    \sum \limits_{i=1}^{n} a_i &= \sum \limits_{i=1}^{n-1} a_i + a_n.   
\end{align}

As an example where induction is used for its proof, 
\begin{equation*}
    \sum \limits_{i=1}^{n} i = \frac{n(n+1)}{2}
\end{equation*}

\pagebreak
\subsubsection{Exercises}
\begin{exercise}[\textbf{1}] Prove the following formulas by induction.
     \begin{enumerate}
         \item $1^2 + \dotsb + n^2 = \dfrac{n(n+1)(2n+1)}{6}$.
         \begin{proof} We induct on $n$. For the base case $n=1$, the equation
         is trivial.
        \begin{align*}
            1^2 &= \frac{1(1+1)(2(1)+1)}{6} \\
            &= \frac{2(3)}{6} \\
            &= 1
        \end{align*}
        Now we assume that the equation hold for arbitrary $n$, and we shall
        prove that it also hold for $n+1$.
        \begin{align*}
            1^2+\dotsb +n^2+(n+1)^2 &= \sum \limits_{i=1} ^{n+1} i^2 \\
            &=  \sum \limits_{i=1} ^{n} i^2 + (n+1)^2 \\
            &= \frac{n(n+1)(2n+1)}{6} + (n+1)^2 \\
            &= \frac{n(n+1)(2n+1)+6(n+1)^2}{6} \\
            &= \frac{(n+1)[2n^2+n+6n+6]}{6} \\
            &= \frac{(n+1)(n+2)(2(n+1)+1)}{6}.
        \end{align*}
        Hence, the equation hold for all natural numbers.
         \end{proof}
         \item $1^3+\dotsb +n^3 =(1+\dotsb +n)^2$.
         \begin{proof} We induct on $n$ and prove the base case $n=1$,
              \begin{equation*}
                  1^3 = (1)^2
              \end{equation*}
              which is trivial. 
              
              Let us now assume that the equation hold for
              arbitrary $n$. We must now show that it also hold for $n+1$.
              \begin{align*}
                  (1+\dotsb +(n+1))^2 &= (n+1)(2(1+\dotsb +n)+(n+1)) + (1+\dotsb +n)^2 \\
                  &= (1^3+\dotsb +n^3)+(n+1)(2(1+\dotsb +n)+(n+1)) \\
                  &= (1^3+\dotsb +n^3) + (n+1)(2\cdot \frac{n(n+1)}{2}+n+1) \\
                  &= (1^3+\dotsb +n^3) + (n+1)((n+1)(n+1)) \\
                  &= 1^3+\dotsb +(n+1)^3,
              \end{align*}
              hence, the equation holds for all natural numbers.
         \end{proof}
     \end{enumerate}
\end{exercise}
\begin{exercise}[\textbf{2}] Find a formula for 
     \begin{enumerate}
        \item $\sum \limits_{i=1} ^{n} (2n-1) = 1+3+5+\dotsb +(2n-1)$.
        \begin{proof}We can make use of the properties of the summation symbol
        and we can easily derive the formla. However, we will not make use of it.
             \begin{align*}
                \sum \limits_{i=1} ^{n} (2n-1) &= 1+3+5+\dotsb +(2n-1) \\
                &= 1+2+3+\dotsb +(2n) - 2(1+2+3+\dotsb +n) \\
                &= \frac{2n(2n+1)}{2} - 2\cdot \frac{n(n+1)}{2} \\
                &= n((2n+1)-(n+1)) \\
                &=n^2.
             \end{align*}
        \end{proof}
        \item $\sum \limits_{i=1} ^{n} (2n-1)^2 = 1^2+3^2+5^2+\dotsb +(2n-1)^2$.
        \begin{proof} We can make use of the properties of the summation symbol
            and we can easily derive the formla. However, we will not make use of it.
             \begin{align*}
                \sum \limits_{i=1} ^{n} (2n-1)^2 &= 1^2+3^2+5^2+\dotsb +(2n-1)^2 \\
                &= 1^2+2^2+3^2+\dotsb +(2n)^2 - 4(1^2+2^2+3^2+\dotsb +n^2) \\
                &= \frac{2n(2n+1)(4n+1)}{6} - 4\cdot \frac{n(n+1)(2n+1)}{6} \\
                &= \frac{2n(2n+1)\left(4n+1-2(n+1)\right)}{6} \\
                &= \frac{n(2n+1)(2n-1)}{3}.
             \end{align*}
        \end{proof}
     \end{enumerate}
\end{exercise}
\pagebreak
\begin{exercise}[\textbf{3}] If $0\leq k \leq n$, the \emph{"binomial
    coefficient"} $\dbinom{n}{k}$ is defined by 
    \begin{equation*}
        \binom{n}{k} = \frac{n!}{k!(n-k)!} = \frac{n(n-1)\dotsb (n-k+1)}{k!}, \text{if }k\neq 0, n 
    \end{equation*}
     and a special case of the first formula if we define $0!=1$,
     \begin{equation*}
         \binom{n}{0}=\binom{n}{n}=1,
     \end{equation*}    
     and for $k<0$ or $k>n$ we just define the binomial coefficient to be $0$.
     \begin{enumerate}
         \item Prove that
         \begin{equation*}
             \binom{n+1}{k}=\binom{n}{k-1}+\binom{n}{k}.
         \end{equation*}
         \begin{proof} It is just a manipulation of the expressions and from the fact that,
            \begin{equation*}
                \binom{n+1}{k} = \frac{(n+1)!}{(n+1-k)!k!}.
            \end{equation*}
            Now for the proof,
              \begin{align*}
                \binom{n}{k-1}+\binom{n}{k} &= \frac{n!}{(n+1-k)!(k-1)!} +\frac{n!}{(n-k)!k!}\\
                  &= \frac{n!k+n!(n+1-k)}{(n+1-k)!k!} \\
                  &= \frac{(n+1)!}{(n+1-k)!k!}.
              \end{align*}
         \end{proof}
         This relation gives rise to the following configuration, known as
         \emph{"Pascal's Triangle"}\textemdash  a number not on one of the sides
         is the sum of the two numbers above it; the binomial coefficient
         $\dbinom{n}{k}$ is the $(k+1)$st number in the $(n+1)$st row.
         \item Notice that all the numbers in Pascal's Triangle are natural
         numbers. Use part (i) to prove by induction that $\dbinom{n}{k}$ is
         always a natural number.
         \begin{proof} We want to prove the assertion that for fixed $n$ (Note: The case $k=0$ is trivial),
            \begin{equation*}
                \binom{n}{k} \text{is a natural number for all }k, 1\leq k \leq n.
            \end{equation*}
            We prove it by induction on $n$. For the base case where $n=1$, we
            only need to prove for $k=1$.
            \begin{equation*}
                \binom{1}{1} =1.
            \end{equation*}
            For the inductive step, we assume that the assertion is true for
            arbitrary $n$ and we will show that 
            \begin{equation*}
                \binom{n+1}{k} \text{ is a natural number for all }k, 1\leq k\leq n+1.
            \end{equation*}
            The case where $k=1$ and $k=n+1$ are trivial. We can now assume that
            for $2\leq k\leq n$, it must be that  $1\leq k-1< k\leq n$ and we
            can make use this with part (i)
            \begin{equation*}
                \binom{n+1}{k} = \binom{n}{k-1}+\binom{n}{k}, 
            \end{equation*}
            since the sum of naturals is a natural, $\binom{n+1}{k}$ is
            natural. We have shown that $\binom{n+1}{k}$ is natural for
            all $k$, $1\leq k \leq n+1$ if $\binom{n}{k}$ is natural for all k
            $1\leq k \leq n$. Hence, the induction is complete.
         \end{proof}
         \item Give another proof that $\dbinom{n}{k}$ is natural number by
         showing that $\dbinom{n}{k}$ is the number of sets of exactly $k$
         integers each chosen from $1,\dotsc , n$.
         \begin{proof} In choosing $k$ objects from $n$, there are $n(n-1)\dotsb
         (n-k+1)$ ways to choose a set with $k$ elements, $\{k_1,\dotsc, k_n
         \}$. However, for each set the $k$ objects can be arranged in $k!$
         ways, that is why we divide by $k!$ as the order of the $k$th element
         in a certain set with the same elements does not matter. Hence, 
         \begin{equation*}
             \binom{n}{k} = \frac{n(n-1)\dotsc (n-k+1)}{k!} = \frac{n!}{(n-k)!k!},
         \end{equation*}
              is the number of sets of exactly $k$ integers chosen from $n$ and
              that is why $\binom{n}{k}$ is always a natural.
         \end{proof}
         \pagebreak
         \item Prove the \emph{Binomial Theorem}: If $a$ and $b$ are any
         numbers and $n$ is a natural number, then 
         \begin{align*}
             (a+b)^n &= a^n+\binom{n}{1}a^{n-1}b+\binom{n}{2}a^{n-2}b^2 +\dotsb +\binom{n}{n-1}ab^{n-1}+b^n \\
             &= \sum \limits_{j=0}^{n}\binom{n}{j}a^{n-j}b^j.
         \end{align*}
         \begin{proof}We prove by induction. For the base case, let $n=1$ in which we get
              \begin{equation*}
                  (a+b)^1=a+b = \binom{1}{0}a+\binom{1}{1}b = \sum\limits_{j=0}^{1}\binom{1}{j}a^{1-j}b^j.
              \end{equation*}
              For the inductive step, we assume that the property holds for
              arbitrary $n=k$. We now show that it also holds for $n=k+1$.
              \begin{align*}
                  (a+b)^{k+1}&=(a+b)\sum\limits_{j=0}^{k}\binom{k}{j}a^{k-j}b^{j} \\
                  &= \left( \sum\limits_{j=0}^{k}\binom{k}{j}a^{(k+1)-j}b^{j} \right)+ \left(\sum\limits_{j=1}^{k+1}\binom{k}{j-1}a^{(k+1)-j}b^{j}\right) \\
                  &= \left( a^{k+1}+\sum\limits_{j=1}^{k}\binom{k}{j}a^{(k+1)-j}b^{j}\right) +\left( b^{k+1}+\sum\limits_{j=1}^{k}\binom{k}{j-1}a^{(k+1)-j}b^{j}\right) \\
                  &= a^{k+1}+b^{k+1}+\sum\limits_{j=1}^{k}\binom{k}{j}a^{(k+1)-j}b^{j} + \binom{k}{j-1}a^{(k+1)-j}b^{j} \\
                  &= a^{k+1}+b^{k+1}+\sum\limits_{j=1}^{k} (a^{(k+1)-j}b^{j})\left( \binom{k}{j}+\binom{k}{j-1}\right) \\ 
                  &= a^{k+1}+b^{k+1}+\sum\limits_{j=1}^{k} (a^{(k+1)-j}b^{j}) \binom{k+1}{j} \\
                  &= \sum\limits_{j=0}^{k+1} (a^{(k+1)-j}b^{j}) \binom{k+1}{j}.
              \end{align*}
         \end{proof}
         \begin{remark}
         To better understand it, an expression $(a^n+\dotsb+b^n)$ have $n+1$
         terms and if multiplied by $(a+b)$, the resulting expression will have
         $2n+2$ terms. The ``ends'' of the expression, $a^{n+1}$ and $b^{n+1}$
         represent the two terms, while the $2n$ terms will be reduced to $n$
         terms. The first sum $^1 a(a^n+\dotsb b^n)$ will have its
         $2$nd-$(n+1)$th term match the $1$st-$n$th term of the second sum $^2
         b(a^n+\dotsb b^n)$. The two sums have the same indexing of the terms
         (The coefficient is dependent on the $i$th index), hence the coefficient
         $\tbinom{n}{k}$ of these terms differ, since the $k$th term of the
         first sum, except for the "end" terms, will match to the $(k-1)$th term
         of the second term.
         \end{remark}
         \item Prove that 
         \begin{enumerate}
             \item $\sum\limits_{j=0}^{n}\binom{n}{j}=\binom{n}{0}+\dotsb+\binom{n}{n}=2^n$.
             \begin{proof}To be continued...
                  
             \end{proof}
         \end{enumerate}
    \end{enumerate}
\begin{exercise}[$\vec{4}$] 
     \begin{enumerate} Prove the following:
         \item Prove that
         \begin{equation*}
             \sum\limits_{k=0}^{l}\binom{n}{k}\binom{m}{l-k}=\binom{n+m}{l}.
         \end{equation*}
         Hint: Apply the binomial theorem to $(1+x)^n(1+x)^m$.

         \begin{proof}We apply the binomial theorem to get 
              \begin{equation*}
                  \sum\limits_{k=0}^{n}\binom{n}{k}x^k\sum\limits_{j=0}^{m}\binom{m}{j}x^j =\sum\limits_{l=0}^{n+m}\binom{n+m}{l}x^l.
              \end{equation*}
              The LHS and RHS are both polynomials, and notice that if
              polynomials are equal, then the coefficients of each term with the
              same degree is equal. We just find another form of the LHS that
              seperates the coefficient of each term so that we can equate the
              coefficient to the RHS.
              \begin{equation*}
                \sum_{l=0}^{n+m} \Bigg( \sum_{\substack{0\le k\le n\\0\le j\le m\\k+j=l}} \binom{n}{k} \binom{m}{j}\Bigg) x^l = \sum_{l=0}^{n+m} \binom{n+m}{l} x^l.
              \end{equation*}
              Then, $k+j=l$ and $j=l-k$ , we find
              \begin{equation*}
                \sum_{l=0}^{n+m} \Bigg( \sum_{k=0}^l \binom{n}{k} \binom{m}{l-k}\Bigg) x^l = \sum_{l=0}^{n+m} \binom{n+m}{l} x^l.
              \end{equation*}
              We can now compare the coefficients and we see that 
              \begin{equation*}
                \sum_{k=0}^l \binom{n}{k} \binom{m}{l-k} = \sum_{l=0}^{n+m} \binom{n+m}{l} x^l.
              \end{equation*}
         \end{proof}
         \begin{remark} The proof/idea is taken from
            \url{https://math.stackexchange.com/a/3950826}, and further discussions
            can be found on \url{https://math.stackexchange.com/a/3950826}.         
            \end{remark}
         \item Prove that
         \begin{equation*}
             \sum\limits_{k=0}^{n}\binom{n}{k}^2=\binom{2n}{n}.
         \end{equation*}
     \end{enumerate}
\end{exercise}
    \begin{exercise}[$\vec{8}$] Prove that every natural number is either even or odd.
        \begin{proof} We prove by induction. For $n=1$, it is trivial since $1$ is odd.
             Now, we assume that for arbitrary $k\in N$, it is either even or odd. 
             \begin{itemize}
                 \item If $k$ is even, so $k=2c$ for some $c\in \Z^+$, then
                 $k+1=2c+1$ which is odd.
                 \item If $k$ is odd, so $k=2d+1$ for some $d\in \Z^+$, then
                 $k+1=2(c+2)$ and we know that $c+2\in \Z^+$, hence $k+1$ is
                 even.
             \end{itemize}
             We have shown that if $k$ is either even or odd, then $k+1$ is also
             even or odd. The induction is complete.
        \end{proof}
    \end{exercise}
\end{exercise}
